# Reproducible Research: Peer Assessment 1

---
title: "Reproducible Research: Peer Assessment 1"
output: PA1_template.md
  html_document: PA1_template.html
    keep_md: true

```{r}
wd <- "C:\\data\\RepData_PeerAssessment1"
setwd(wd)
getwd()

library(ggplot2)
```

## Loading and preprocessing the data

```{r}
file <- "C:\\data\\RepData_PeerAssessment1\\activity.csv"
dat <- read.table(file, header = TRUE, sep = ",", na.strings = "NA", stringsAsFactors = FALSE)
dat2 <- tapply(dat$steps, dat$date, sum)
dat3 <- as.data.frame(dat2)
dat$date <- as.Date(dat$date)
```
## What is mean total number of steps taken per day?

```{r}
names(dat3) <- c("steps")
mean <- mean(dat3$steps, na.rm = TRUE)
median <- median(dat3$steps, na.rm = TRUE)
qplot(dat3$steps, main = "Total Number of Steps Taken Each Day", xlab = "Steps Taken Each Day")
```


The mean and median total number of steps taken per day are `r mean` and `r median` seperately.

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
